TBD

### 2016-09-27 paper.tex
LINCAL revamp

\subsection{LINCAL}
\begin{equation}
c_{ij} = y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}
\end{equation}

>>>>

\subsection{LINCAL}
Assume that $\eta_i,\eta_j,\eta_{\phi_{ij}},\varphi_i,\varphi_j$ and $\varphi_{\phi_{ij}}$ are real valued variables.
Let us once again ignore the noise term of Eq.~\eqref{eq:vis_red}. Substituting $g_i$ with $e^{\eta_i - i \varphi_i}$, $g_j$ with $e^{\eta_j - i \varphi_j}$ and $y_{\phi_{ij}}$ with $e^{\eta_{\phi_{ij}}- i \varphi_{\phi_{ij}}}$ in Eq.~\eqref{eq:vis_red} results in  
\begin{equation}
d_{ij} =  e^{\eta_i - i \varphi_i} e^{\eta_{\phi_{ij}}- i \varphi_{\phi_{ij}}} e^{\eta_j + i \varphi_j}.
\end{equation}
The following partial derivatives are easily computed
